% ======================================================================
% RUN 57 - P-AC: full-length write-out of run-54's staged Props A/C +
% Lemma B (the Cauchy-estimate family-uniformity package for M1 clause
% (ii) gaps (a),(b) of an17:CW-grade), WITH THE FOUR RUN-54 ADVERSARY
% WOUNDS W1-W4 FOLDED IN AS MANDATORY CONDITIONS. Each fix is marked
% [W-k FIX] at its locus. Source: eo_attack.tex (run 54, arm A2) +
% ledger_run54.md R-arm wound list (verbatim). The sqrt(n)-polyradius
% parenthetical owed by run-54 R is included at EP1'.
% GRADE DISCIPLINE: this file does NOT close clause (ii); the verdict
% is stated modulo the run-54 modulo-list OF RECORD (the R-arm list,
% one item longer than A2's printed list). Clause (ii)/M1 remains
% PLAUSIBLE. Paper-preamble-compatible fragment; compile check via
% port_ac_wrap.tex. ZERO writes to the three protected files.
% Labels prefixed pac: to avoid collisions.
% ======================================================================

\subsection*{P-AC. The family-uniformity package for clause (ii):
Propositions A and C and Lemma B, written out}

\paragraph{Scope and wiring (read first).} Target: the two printed gaps
of Rem.\ an17:CW-grade (appendix l.3394--3402): \textup{(a)} the $N{=}2$
finite-regularity Hadamard-parametrix \emph{construction} with
quantitative $v_2$, family-uniform over the ball, not in print;
\textup{(b)} the exact multi-index constant-tracking through the $N{=}2$
commutator source and the Tice estimate, not executed. On the analytic
class $U_\omega$ both are discharged \emph{as family-uniformity
questions} below; what survives is the modulo-list,
restated in Theorem~\ref{pac:thm-verdict}. \textbf{Wiring order
[W1]:} Proposition~\ref{pac:prop-A} $\to$
Proposition~\ref{pac:prop-C} $\to$ Theorem~\ref{pac:thm-verdict} $\to$
Lemma~\ref{pac:lem-B}. Lemma~\ref{pac:lem-B} (the seed triangle for
$W_*$) is \emph{consumer-facing only}: it is stated \emph{after} the
$C_W$ chain closes and is cited by \emph{no} proposition of this
package. The in-ladder spectator sups of
Proposition~\ref{pac:prop-C} are wired to the single-metric route
(an17:Nc-corrected's own uniform analogue $+$ an17:DoD transport,
$(D0)$-gated), \emph{never} to Lemma~\ref{pac:lem-B} --- citing
Lemma B there would be circular (Lemma B derives
$W_*$ \emph{from} $C_W$), so that wiring is avoided here.

\paragraph{The four conditions folded into the package.}
\begin{itemize}[leftmargin=*,nosep]
\item[\textup{W1}] \emph{Circular wiring} (a naive Prop.\ C would cite Lemma
  B for in-ladder spectator sups; Lemma B derives $W_*$ from $C_W$).
  Fix: the wiring order above; spectator sups re-routed at
  Prop.~\ref{pac:prop-C}(C3). Marked there.
\item[\textup{W2}] \emph{\#B$'$ omitted} (the appendix books
  lem:W2star gated by $(D0)$ \emph{and} \#B$'$, l.3325--3327 and
  l.3951--3952; listing only $(D0)$ would be incomplete). Fix: \#B$'$
  restored to the modulo-list with its conditional discharge sentence,
  Rem.~\ref{pac:rem-Bprime}. Marked there.
\item[\textup{W3}] \emph{Grade inheritance} (``$C_{\Delta_2}=0$ on
  BFV'' lives inside an17:Nc-corrected, printed grade ``PLAUSIBLE
  \dots NEVER cited at THEOREM grade'', l.3289--3293; citing it bare
  would drop that grade). Fix: every BFV-vanishing citation below carries the
  carrier grade and the revival condition. Marked at each use.
\item[\textup{W4}] \emph{Seed tag} (a bare Lemma B would label
  $W_*^{\mathrm{seed}}$ ``THEOREM''; the verdict's own residue (res1)
  makes it $(D0)$-gated at the $b{=}1$ slot). Fix:
  Lemma~\ref{pac:lem-B} tags it ``THEOREM modulo $(D0)$''. Marked
  there.
\end{itemize}

\begin{lemma}[EP1$'$: spacetime polydisc Cauchy estimates, with the
$\sqrt n$ polyradius made explicit]\label{pac:lem-EP1}
Let $g\in U_\omega$, $F:=g-g_0$ (components $F_{ab}$, holomorphic on
$\mathcal K_{\rho_a}=\{z\in\mathbb C^n:\operatorname{dist}(z,K'')<
\rho_a\}$, $\|F\|_{\mathcal K_{\rho_a}}\le\varepsilon_a$). Then for
every multi-index $\alpha$ and every $z_0$ with
$\operatorname{dist}(z_0,K'')\le\rho_a/2$,
\begin{equation}\label{pac:eq-EP1}
  |\partial^\alpha F(z_0)|\;\le\;\alpha!\,
  \Bigl(\frac{2\sqrt n}{\rho_a}\Bigr)^{|\alpha|}\varepsilon_a ,
  \qquad\text{hence}\quad
  \sup_{U_\omega}\ \sup_{\overline{\mathcal K_{\rho_a/2}}}
  |\partial^\alpha(g-g_0)|\le\alpha!\,
  \Bigl(\frac{2\sqrt n}{\rho_a}\Bigr)^{|\alpha|}\varepsilon_a .
\end{equation}
\emph{(The owed $\sqrt n$ parenthetical: the collar is a chart-Euclidean
tube in $\mathbb C^n$, so the largest polydisc centred at $z_0$ and
contained in $\mathcal K_{\rho_a}$ has polyradius
$(\rho_a/2)/\sqrt n$ per coordinate --- a corner of a polydisc of
polyradius $r$ lies at Euclidean distance $r\sqrt n$. A naive
EP1 displays $(2/\rho_a)^{|\alpha|}$, and the appendix's own
an17:lem-embed proof (l.166--175) says ``polydisc of radius $\rho_a$'';
both are constant-level slips with no structural effect --- the
appendix absorbs its version into the unspecified
$C_{\mathrm{cw}}(K'',n,s)$, so nothing printed is false --- but every
EP1-derived constant below carries the honest $\sqrt n$.)}
\end{lemma}
\begin{proof}
The polydisc $P(z_0;r,\dots,r)$, $r=\rho_a/(2\sqrt n)$, satisfies
$\sup_{w\in P}|w-z_0|\le r\sqrt n=\rho_a/2$, so
$P\subset\mathcal K_{\rho_a}$ when
$\operatorname{dist}(z_0,K'')\le\rho_a/2$. The iterated one-variable
Cauchy inequality on $P$ gives
$|\partial^\alpha F(z_0)|\le\alpha!\,r^{-|\alpha|}
\sup_P|F|\le\alpha!\,(2\sqrt n/\rho_a)^{|\alpha|}\varepsilon_a$.
This is the appendix's own method (an17:lem-embed, printed site
l.166--175), iterated to all orders: ball-uniform $C^k$ bounds for
\emph{every} $k$ with geometric constants in $(\rho_a,\varepsilon_a,n)$
alone --- no Sobolev index, no $C^k$ norm of a sample metric. It is
the licensed analytic tool of the package (spacetime variable only;
the EP0/EP2 fences remain in force: nothing below
differentiates in $g$, and no difference estimate routes through the
collar).
\end{proof}

\begin{proposition}[A: the (N-a) parametrix package is family-uniform
over $U_\omega$ --- gap (a) discharged on the analytic class]
\label{pac:prop-A}
Let $U_\omega=U_\omega(g_0,\rho_a,\varepsilon_a)$, $n=4$, $s>11$,
$K\subset\mathcal M$ compact. There exist $\delta_c^{\mathbb C}>0$ and
constants $\Lambda_0,\Lambda_1,\Lambda_2,
C^{\mathrm{fam}}_{v_2}$, all functions of
$(g_0,\rho_a,\varepsilon_a,K,\textup{atlas})$ alone, such that for all
$g,g'\in U_\omega$:
\begin{enumerate}[label=\textup{(A\arabic*)},leftmargin=*,nosep]
\item (uniform normal geometry, holomorphic) every $x\in K$ has a
  $g$-convex normal chart of radius $\ge\delta_c$ (the an17:G radius),
  and $\sigma_g,\Delta^{\pm1/2}_g$ exist on the bi-collar
  $V_{\delta_c}$, are real-analytic, and extend holomorphically to the
  uniform complex bi-collar
  $\mathcal V^{\mathbb C}:=\{(z,w):z\in\mathcal K_{\rho_a/4},\
  |w-z|<\delta_c^{\mathbb C}\}$ with
  $\sup_{U_\omega}\sup_{\mathcal V^{\mathbb C}}
  \bigl(|\sigma_g|+|\Delta^{\pm1/2}_g|\bigr)\le\Lambda_0$;
\item (quantitative $v_k$, all orders from one sup) the Hadamard
  coefficients $v_0,v_1,v_2$ of the transport recursion
  (\cite[Thm.~2.1]{Moretti2003}, cited in print at appendix
  l.3208--3210) exist on $V_{\delta_c}$, extend holomorphically to
  $\mathcal V^{\mathbb C}$, and satisfy, for every bi-multi-index
  $\beta$,
  \[
    \sup_{U_\omega}\ \sup_{\mathcal V^{\mathbb C}_{1/2}}
    |\partial^\beta v_k[g]|\;\le\;
    \beta!\,\Bigl(\frac{4\sqrt{2n}}{\min(\rho_a,\delta_c^{\mathbb C})}
    \Bigr)^{|\beta|}\Lambda_k
    \qquad(k\le2),
  \]
  ($\mathcal V^{\mathbb C}_{1/2}$ the half bi-collar; the $\sqrt{2n}$
  is EP1$'$ in the $2n$ complex bi-variables); in particular the
  consumed registers $v_2\in H^{s-6}$, $\square_gv_2\in H^{s-8}$ of
  (N-a-NF) hold with ball-uniform norms
  $\le C^{\mathrm{reg}}_{v_2}:=c(s)\,|V_{\delta_c}|^{1/2}
  \max_{|\beta|\le s}\beta!\,(4\sqrt{2n}/\min(\rho_a,
  \delta_c^{\mathbb C}))^{|\beta|}\Lambda_2$;
\item (difference legs at the Lipschitz rate, real side only) for the
  same registers,
  \[
    \|v_k[g]-v_k[g']\|_{H^{s-2k-2}(V_{\delta_c})}
    +\|\square_gv_2[g]-\square_{g'}v_2[g']\|_{H^{s-8}(V_{\delta_c})}
    \;\le\;C^{\mathrm{fam}}_{v_2}\,\|g-g'\|_{H^s};
  \]
\item (normal form) the glued $N{=}2$ residual has the printed normal
  form (N-a-NF) (appendix l.3213--3218):
  $S'_2=(\square_{g'}v'_2)\,\sigma_{\mathrm{geo}}^2
  \log\sigma_{\mathrm{geo}}+R_{\mathrm{sm}}$, pair $(8,6)$,
  $R_{\mathrm{sm}}$ strictly softer, all constants ball-uniform.
\end{enumerate}
\end{proposition}
\begin{proof}
\emph{(A1).} The ball-uniform \emph{real} convex-normal radius
$\delta_c$ is in print at THEOREM grade: an17:G, l.3233--3236
(Chen--LeFloch / Cheeger--Gromov--Taylor from $g_0$-data and
$\sup_{U_\omega}\|g\|_{H^s}$). For the holomorphic extension: on
$\mathcal K_{\rho_a/2}$ the Christoffels $\Gamma[g]$ are holomorphic
with $M_\Gamma:=\sup_{U_\omega}\|\Gamma[g]\|_{\mathcal K_{\rho_a/2}}
<\infty$ --- this is the appendix's own analytic-ODE package,
an17:rem-CK (printed site l.465--482, display an17:eq-MGamma; the
denominators carry $|\det g|\ge d_\omega$, l.142--150), which Part (A)
of the appendix already consumes (rem:an17-orthogonal: Part (A)
``cites only $(R1),(R3),(R4),(R5),F2$ and the holomorphic-ODE
package''). The complex geodesic flow $\ddot\gamma=-\Gamma[g](\dot
\gamma,\dot\gamma)$ with data $(z,\xi)$, $z\in\mathcal K_{\rho_a/4}$,
$|\xi|\le2\delta_c^{\mathbb C}$, has a holomorphic solution on
$t\in[0,1]$ by the uniform-strip Picard iteration an17:prop-strip
(printed site l.484--500), provided
$\delta_c^{\mathbb C}\le c\,(1+M_\Gamma)^{-1}\min(\rho_a/4,\delta_c)$
--- one displayed shrink, ball-uniform. Holomorphy of
$(z,\xi)\mapsto\gamma$ is Picard's uniform limit of holomorphic
iterates. The exponential Jacobian $\partial\xi/\partial w$ at
$\xi=\exp_z^{-1}(w)$ equals $\mathbb 1+O(\delta_c^{\mathbb C}
M_\Gamma)$, invertible after one more displayed shrink; then
$\sigma_g(z,w)=\tfrac12 q_{g,z}(\xi,\xi)$ and
$\Delta^{1/2}_g=|\det g(z)|^{-1/4}|\det g(w)|^{-1/4}
|\det(-\partial_z\partial_w\sigma_g)|^{1/2}$ are holomorphic with
$\Lambda_0:=c\,(1+\varepsilon_a+\|g_0\|_{\mathcal K_{\rho_a}})
(1+M_\Gamma)^2(\delta_c^{\mathbb C})^2+c\,d_\omega^{-1/2}
(1+M_\Gamma)^{2}$; non-vanishing of $\Delta^{1/2}$:
$\Delta^{1/2}=1+O(\sigma)$ with the $O$ Cauchy-bounded via EP1$'$ on
its bi-collar Hessian, so a final displayed shrink of
$\delta_c^{\mathbb C}$ gives $|\Delta^{1/2}|\ge\tfrac12$ on
$\mathcal V^{\mathbb C}$, ball-uniformly.
\emph{(A2).} The recursion $2\nabla\sigma\!\cdot\!\nabla v_k+
(\square\sigma-2n+4k)v_k=-\square v_{k-1}$ is, along the (A1)
holomorphic geodesics in the rescaled radial variable, a
\emph{linear} regular-singular ODE $(2r\partial_r+A_k)v_k=f_k$ with
holomorphic coefficients bounded by $c\Lambda_0$ on
$\mathcal V^{\mathbb C}$ and indicial root $4k>0$ ($k\ge1$; $k=0$
transports $\Delta^{1/2}$-data), and source $f_k$ a universal
polynomial in $(\partial^{\le2}\sigma,\Delta^{\pm1/2},
\partial^{\le2k+2}g,g^{-1})$ --- every factor holomorphic and
EP1$'$-bounded on $\mathcal V^{\mathbb C}$. Gronwall along the radial
integral gives the \emph{single} sup bound
$\sup_{\mathcal V^{\mathbb C}}|v_k|\le\Lambda_k:=
c\,e^{c\Lambda_0\delta_c^{\mathbb C}}\,
P_k\bigl(\Lambda_0,M_\Gamma,d_\omega^{-1},
(2\sqrt n/\rho_a)^{2k+2}(2k+2)!\,\varepsilon_a
+\|g_0\|_{C^{2k+2}}\bigr)$, $P_k$ a displayed universal polynomial
(finite recursion, $k\le2$). \emph{One} sup bound then generates every
derivative bound: the iterated Cauchy estimate of EP1$'$ in the $2n$
bi-collar variables on $\mathcal V^{\mathbb C}$ gives the displayed
all-order form --- this is where analyticity replaces the entire
multi-index tape of gap (b) at the construction level. Restricting to
the real points and integrating over $V_{\delta_c}$ yields the
$H^{s-6}/H^{s-8}$ register bounds with $C^{\mathrm{reg}}_{v_2}$ as
displayed ($\square_g$ costs two more Cauchy derivatives and one
$g^{-1}$-factor, absorbed).
\emph{(A3).} Real side. The difference legs never touch the collar
(EP2): they are the Gronwall/Christoffel-difference transport route,
now \emph{ported in full} as P-M3 Lemmas L1--L3 (port:lem-gamma / port:lem-sigma / port:lem-vk: the exact identity
$\delta\Gamma=\tfrac12g^{-1}(\nabla'h+\nabla'h-\nabla'h)$, flow
Gronwall, transport Duhamel --- a standard derivation, here
re-derived with explicit constants), upgraded from $C^0$- to
$H^{s-2k-2}$-difference norms by the linearity of the transport
average in its top curvature-polynomial argument, which is in print at
the (N-a) block (appendix l.3219--3222:
$\|h_g-h_{g'}\|_{H^a}\le C_{\mathrm{poly}}\|g-g'\|_{H^s}$, with
$C_{v_2}=\tfrac1{12}\kappa_\Delta C_{\mathrm{poly}}$): lower-order
factors are estimated by the (A2) sup bounds, the top jet enters
linearly, so
$C^{\mathrm{fam}}_{v_2}:=c\,C_{\mathrm{poly}}\,
e^{c\Lambda_0\delta_c}\,\bigl(1+\Lambda_2\bigr)^2
\bigl(1+\kappa_\Gamma(1)+\kappa_S\bigr)$ with
$\kappa_\Gamma,\kappa_S$ the displayed P-M3 constants (in the
corrected difference-count form
$\kappa_\Gamma(k)=c_k(n)\Lambda_U^{2k+7}d_U^{-2(k+1)}$). All placements
are Morrey/Banach-algebra at $s>11$ on the real side.
\emph{(A4).} Gluing: an17:G(ii)--(v) is THEOREM in print
(l.3233--3254) and consumes exactly (A2)--(A3): defect legs book
$(8,\infty)$, the main rung $(8,6)$ (N-a-NF), the log-branch
cancellation on overlaps is patch-independent geometry with the one
global scale $\ell$, and every constant scales linearly in the
multiplicity $m(K)$ (an17:G(iv), no Besicovitch). Nothing in this
proof estimates anything not already named. \qedhere
\end{proof}

\begin{remark}[What (A) does not do]\label{pac:rem-A-scope}
It never touches the state ($\omega^{(2)}_g$ enters only through the
data/spectator routes of Prop.~\ref{pac:prop-C}(C3) and the verdict's
residues); it makes no $H^s$-open statement (F-iii respected: sups and
pair-moduli over $U_\omega$ only); it never continues across a shock
(every object lives on the fixed collar of real-analytic members;
Barrab\`es--Israel metrics are outside $U_\omega$; Guard F-shock,
unification.tex l.17172--17185); and it asserts \emph{no} analyticity
in the metric parameter (EP0): every $g$-difference is real-side
Lipschitz, never a collar conversion (EP2's H\"older-only
counterexample stands as the fence).
\end{remark}

\begin{proposition}[C: gap (b) vacates over $U_\omega$ to the printed
register arithmetic; the spectator sups correctly routed]\label{pac:prop-C}
Grant Proposition~\ref{pac:prop-A}. Consider the ladder source
$f_2=-(S_{g,2}-S_{g',2})-(\square_g-\square_{g'})W_{g',2}$ and the
Rung-4 slice products of the two ladders (an17:slice-ladder,
an17:slice-ladder-4d --- THEOREM over $U_\omega$ at their printed
sites). Then:
\begin{enumerate}[label=\textup{(C\arabic*)},leftmargin=*,nosep]
\item every constant appearing in the ladders' estimates of $f_2$ and
  of the Rung-4 products is a polynomial in the finite named list
  \[
    \Bigl\{\alpha!\bigl(\tfrac{2\sqrt n}{\rho_a}\bigr)^{|\alpha|}
    \varepsilon_a\ (|\alpha|\le s{+}1);\ \Lambda_0,\Lambda_1,\Lambda_2;
    \ C^{\mathrm{fam}}_{v_2};\ d_\omega^{-1};\ Q_*,P_*,T_c;\
    c^{\mathrm{Mor}},c_{\mathrm{mult}},c_{\mathrm{tr}},
    c_{\mathrm{alg}},c_\Pi,c_{\mathrm{fol}};\ m(K),L_\chi\Bigr\},
  \]
  each entry ball-uniform and named in print or in
  Prop.~\ref{pac:prop-A} (EP1$'$; an17:DoD l.3256--3268 for
  $Q_*,P_*,T_c$; the ladder constant display and its provenance note,
  appendix l.3010--3035, for
  $c_{\mathrm{mult}},c_{\mathrm{tr}},c_{\mathrm{alg}},c_\Pi,
  c_{\mathrm{fol}},c^{\mathrm{Mor}}$; an17:G(i),(iv) for
  $m(K),L_\chi$);
\item consequently the \emph{content} of gap (b) over $U_\omega$ is
  not ``track every multi-index constant'' (each is automatically
  ball-uniform by (C1)) but only the finite \emph{term inventory}:
  that $f_2$ and the Rung-4 products contain no term outside the
  booked registers --- and that inventory is in print: the normal form
  (N-a-NF) (Prop.~\ref{pac:prop-A}(A4)), the gluing defect legs
  (an17:G(iii), THEOREM), and the commutator leg
  $(\square_g-\square_{g'})W_{g',2}$, whose coefficients are
  $(g{-}g')$-linear with Banach-algebra placements at $s>11$;
\item \textbf{[W1 --- the spectator sups]} the
  $W_{g',2}$-factor of the commutator leg consumes the
  \emph{single-metric} uniform bounds at the $\partial_y$-slotted
  registers. These are supplied by the \emph{single-metric uniform
  analogue} recorded inside Lem.\ an17:Nc-corrected's own statement
  (l.3280--3281: ``together with the single-metric uniform analogue
  for $W_{g',2}$''), fed through the an17:DoD short-slab data route
  (THEOREM, l.3256--3268) from the seed-adjacent Cauchy data --- and
  those data are exactly the $(D0)$ residue at the $b{=}1$ field slot
  (an17:named-residues, l.3321--3324). They are therefore cited here
  as \emph{$(D0)$-gated inputs}, NOT as Lemma~\ref{pac:lem-B}
  consequences: Lemma~\ref{pac:lem-B} presupposes $C_W$ and may not
  feed this proposition. (Lemma B is \emph{not} cited at this
  locus --- that would be circular; the gate is carried into
  Theorem~\ref{pac:thm-verdict}(res1) instead.)
\end{enumerate}
\end{proposition}
\begin{proof}
(C1) Fix any product term
$T=\prod_j\partial^{\gamma_j}c_j\cdot\partial^\beta u$ appearing in
the first-order reduction of the source or in a Rung-4 slice product
($c_j\in\{a^{\mu\nu},b^\mu,\theta_a,\chi_a,\sigma,\Delta^{\pm1/2},
v_k\}$, $u\in\{D_2,W_{g',2}\}$). The ladders (THEOREM) book $T$'s
\emph{register}; only the constant was open. Every coefficient factor
is a $g$-jet (EP1$'$: ball-uniform at all orders, with the $\sqrt n$),
an atlas/cutoff datum ($L_\chi$, $m(K)$: fixed by an17:G), or a
package biscalar (Prop.~\ref{pac:prop-A}(A1)--(A2): ball-uniform at
all orders). Moser/tame product constants at fixed $s$ are polynomials
in finitely many $C^k$ norms of the coefficients --- all just listed
--- times the universal $c_{\mathrm{mult}}(s),c_{\mathrm{alg}}$; the
energy step contributes the Tice factor $\sqrt{Q_*e^{P_*T_c}}$
(an17:DoD, THEOREM). The list is finite and each entry named, so the
composite is the claimed polynomial. (C2) What this does NOT prove:
completeness of the inventory is \emph{cited}, not re-derived ---
(N-a-NF) + an17:G(iii) + the displayed commutator leg, at their
printed grades. (C3) The re-routing is definitional (which in-print
statement is cited); the mathematical content --- that the
single-metric $\partial_y$-slotted sups exist at the consumed
registers given seed data at the $b{=}1$ slot --- is precisely the
$(D0)$-gated single-metric write-out $W^{(2)}_*$ named at
an17:named-residues; no circular step remains: $C_W$-chain
$\not\ni$ Lemma~\ref{pac:lem-B}. \qedhere
\end{proof}

\begin{remark}[\#B$'$ and its conditional
discharge sentence]\label{pac:rem-Bprime}
The appendix books the single-metric write-out lem:W2star as gated by
$(D0)$ \emph{and} \#B$'$ (the off-collar/across-patches kernel
variant; printed at l.3325--3327 and in the M1 modulo item
l.3951--3952). Accordingly \#B$'$ is listed here as a residue. \emph{The owed discharge sentence,
conditional-tagged:} at the \emph{seed} instance the perturbation
region $P$ is empty, so no patch traversal occurs and \#B$'$ is not
exercised; for general $g'\in U_\omega$ the spectator route runs
entirely from BFV/RCE surface data through the an17:DoD short slab
(no patch traversal), so \#B$'$ is bypassed \emph{if and only if} the
BFV/RCE anchoring identity holds --- i.e.\ this discharge \textbf{[W3]} rides ``$C_{\Delta_2}=0$ on the BFV surface'', whose carrier is
Lem.\ an17:Nc-corrected at printed grade \emph{PLAUSIBLE}
(l.3289--3293: ``NEVER cited at THEOREM grade''), and is therefore
itself only PLAUSIBLE-conditional. \emph{Revival condition:} any
consumer that un-anchors the state family from BFV/RCE re-opens both
(E-env) \emph{and} \#B$'$ at full strength.
\end{remark}

\begin{theorem}[M1 verdict: the family-uniformity content of
clause (ii) closes over $U_\omega$; the honest modulo-list]\label{pac:thm-verdict}
Over $U_\omega$, at $s>11$, grant the printed ladder theorems
(an17:slice-ladder, an17:slice-ladder-4d, an17:G, an17:DoD --- all
THEOREM at their printed sites) and
Propositions~\ref{pac:prop-A} and~\ref{pac:prop-C}. Then clause (ii)
of Hyp.\ hyp:hadamard-uniform-omega holds for the paper's
BFV/RCE-anchored state family, with $C_W(K)$ exactly as assembled at
an17:CW-grade (l.3374--3384) and $W_*(K)$ from
Lemma~\ref{pac:lem-B}, \emph{modulo precisely the following
modulo-list}:
\begin{enumerate}[label=\textup{(res\arabic*)},leftmargin=*,nosep]
\item\label{pac:res1} $(D0)$ --- the seed-adjacent Cauchy-data
  write-out of the single-metric $W_{g_0,2}$ at the $b{=}1$ field slot
  (an17:named-residues l.3321--3324): fixed-metric, \emph{not} a
  uniformity statement; it gates the spectator registers
  $W^{(2)}_*$ of Prop.~\ref{pac:prop-C}(C3) through the data-transport
  route, whose transport constants are ball-uniform (EP1$'$/an17:DoD);
\item\label{pac:res2} \textbf{[W3]} the BFV-vanishing
  ``$C_{\Delta_2}=0$ on the BFV surface'', cited \emph{only} at its
  carrier's printed grade: Lem.\ an17:Nc-corrected, PLAUSIBLE, never
  at THEOREM (l.3289--3293). Where it enters: the
  $C_{\mathrm{trans}}=C_{\mathrm{data}}=0$ simplification of the
  an17:CW-grade assembly and the \#B$'$ bypass of
  Rem.~\ref{pac:rem-Bprime}. Revival: un-anchoring from BFV/RCE
  re-opens (E-env) and \#B$'$;
\item\label{pac:res3} \textbf{[W2]} \#B$'$ --- listed, with its
  conditional discharge sentence in Rem.~\ref{pac:rem-Bprime}
  (BFV-conditional, hence riding \ref{pac:res2});
\item\label{pac:res4} (E-env) --- exercised only \emph{off} the BFV
  anchoring, hence not on the Part-B consumer path for the paper's own
  state class; same carrier grade discipline as \ref{pac:res2}.
\end{enumerate}
The two printed gaps of an17:CW-grade are thereby discharged \emph{as
family-uniformity questions}: (a) by Prop.~\ref{pac:prop-A} (the
construction is classical-Hadamard on analytic metrics, quantitative
by EP1$'$), (b) by Prop.~\ref{pac:prop-C} (every constant
automatically ball-uniform; the term inventory is in print). The
full-length Props~A/C write-out is itself provided here. What blocks the word THEOREM
for clause (ii) as a whole is \ref{pac:res1}--\ref{pac:res2}: a
long-standing fixed-metric data residue, plus one PLAUSIBLE-grade carrier. \emph{\underline{Grade:
clause (ii)/M1 remains PLAUSIBLE.}} No grade line moves with this
write-out alone; and a $(D0)$ closure alone would \emph{not} lift
\ref{pac:res2} (the BFV conditionality survives it).
\end{theorem}

\begin{lemma}[B: seed-anchored triangle --- consumer-facing only,
stated after the $C_W$ chain]\label{pac:lem-B}
Suppose the mixed-jet Lipschitz bound of clause (ii) holds over
$U_\omega$ with constant $C_W(K)$ (Theorem~\ref{pac:thm-verdict},
modulo its list). Let $W^{\mathrm{seed}}_*(K):=
\max_{|a|+|b|\le1\,\cup\,|a|=|b|=1}\sup_{x\in K}
\bigl|[\partial_x^a\partial_y^bW_{g_0,2}](x,x)\bigr|$ --- the seed
mixed jets, finite at $s>10$ (the established single-metric ground truth,
appendix l.2752--2753 and l.3383). \textbf{[W4]}
$W^{\mathrm{seed}}_*(K)$ carries the grade \emph{THEOREM modulo
$(D0)$}: its data feed at the $b{=}1$ slot is exactly
\ref{pac:res1} (a bare THEOREM tag would be inconsistent with it). Then for every
$g\in U_\omega$,
\[
  W_*(K)\;\le\;W^{\mathrm{seed}}_*(K)
  \;+\;C_W(K)\,C_{\mathrm{emb}}\,\varepsilon_a ,
\]
since $\|g-g_0\|_{H^s(K'')}\le C_{\mathrm{emb}}\varepsilon_a$
(an17:lem-embed, l.157--175). Hence the two-constant demand
$\{C_W,W_*\}$ of M1 collapses to the single demand $C_W$ --- the F2
seed-anchored pattern of the paper's own modulus
(lem:E2-energy-lipschitz's triangle, unification.tex l.17438--17443).
\emph{Wiring note [W1]: this lemma is consumed only downstream
(by the clause-(ii) consumers of hyp:hadamard-uniform-omega); no
proposition of this package cites it.}
\end{lemma}

\begin{remark}[Grade discipline; fences; what remains]
\label{pac:rem-grade}
(i) This write-out moves \emph{no} printed grade: clause (ii)/M1 is
PLAUSIBLE before and after; the contribution is that its open content
is now the \emph{written} finite list of Theorem~\ref{pac:thm-verdict}
(all four conditions folded in), not the two unbounded-looking gaps (a),(b).
(ii) Fences: F-diff (both metrics in $U_\omega$ throughout); F-iii
(sups and pair-moduli only, never an $H^s$-open modulus); F-shock
(fixed collar, no continuation); EP2 (no collar-to-$H^s$ conversion
anywhere --- all Lipschitz legs real-side); EP4 (no Montel step
anywhere in this package). (iii) The remaining mathematics is
\ref{pac:res1} ($(D0)$, now closed at the seed by the classical
analytic-convergence lever --- App.~\ref{app:e2a-ports}, the (D0)
port) and the \ref{pac:res2} carrier grade,
which no port can lift (it is a data-side PLAUSIBLE of the appendix
itself). (iv) With this write-out and the clause-(i) port in hand,
an17:CW-grade's gaps (a),(b) may be re-pointed to the
discharge-modulo-list of Theorem~\ref{pac:thm-verdict}.
\end{remark}
% ====================== end of P-AC fragment ==========================
